% Created 2022-10-24 Mon 20:21
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{mathptmx}           % set font type to Times
\usepackage[scaled=.90]{helvet} % set font type to Times (Helvetica for some special characters)
\usepackage{courier}            % set font type to Times (Courier for other special characters)
\author{Gary W. Cox and Eric Magar}
\date{October 18, 2022}
\title{How Much is Majority Status in the U.S. Congress Worth? --- Corrigendum\\\medskip
\large \url{doi:10.2307/2585397}. Published in the \emph{American Political Science Review}, Volume 93, Issue 2, June 1999, pp. 299--309}
\hypersetup{
 pdfauthor={Gary W. Cox and Eric Magar},
 pdftitle={How Much is Majority Status in the U.S. Congress Worth? --- Corrigendum},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.3)}, 
 pdflang={English}}

\begin{document}

\maketitle
\noindent The authors regret the inclusion of an error in the above article. The fourth paragraph in p.\ 302 of the published text reads thus:

\begin{quote}
Our results, presented in Table 1, show that electorally less safe members, those on exclusive committees, those voting more conservatively, and first-termers all received more in receipts from business PACs, other things constant. Only the last effect, however, is statistically discernible from zero.
\end{quote}

\noindent It should say

\begin{quote}
Our results, presented in Table 1, show that electorally less safe members, those on exclusive committees, and those voting more conservatively all received more in receipts from business PACs, other things constant. And sophomores, with $\Delta Frosh_{it}$ scores of $-1$, received less in receipts from business PACs, other things constant. Only the last effect is statistically discernible from zero.
\end{quote}

\bigskip \noindent $\Delta Frosh$ is a control variable in the study and ours was a misinterpretation of the reported estimate (which is correct in the text and table), so the corrigendum has no substantial impact in the findings we report nor in the claims we make. It will interest scholars focused on newcomer members of Congress. The authors are grateful to Scott Ainsworth for pointing our failure to take the cross-temporal perspective when interpreting this coefficient. We appologize for this error.
\end{document}
